### 2014-11-11 tex/bisimulation.tex
Added heap properties

Let $p \rgse p^\prime$ be defined as a union over state relations:
$$
\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E\cdot} \cup \rgse^\com
$$
where \emph{A} is a field access $\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
\rightarrow \cfgnt{k}\rp$, \emph{W} is a field write $\lp
\cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
\cfgnt{k}\rp$, \emph{E} is a reference compare $\lp
\cfgnt{v}\ \cfgt{=}\ \cfgnt{*} \rightarrow \cfgnt{k}\rp$, $\cdot$
indicates a null reference in the operation or a false outcome, and
\emph{\com} is everything else in the language. Any state relation, say $\rightarrow_x$, is trivially extended to sets of states as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
$$
Let $\hookrightarrow_\gse$ be the extension of $\rgse$ to sets of states.
$$
\rsgse = \hookrightarrow_\gse^\mathit{A}
\cup \hookrightarrow_\gse^\mathit{A\cdot} \cup \hookrightarrow_\gse^\mathit{W} \cup
\hookrightarrow_\gse^\mathit{W\cdot} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E\cdot}
\cup \hookrightarrow_\gse^\com
$$
The definition embodies the notion of splitting equivalence classes at
certain operations. The set $P$ at a field access for example has two
potential successors: a non-null and null reference. Respectively, the
set $P \rgse^\com P^\prime$ only has a single successor since those expressions
are not related to control flow.

@@

\begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisumlation.
\label{lem:access}
$$
\forall P \in 2^{S_\mathit{FA}}\ (P \sqsubset q \Rightarrow (P\ q) \in F_\sim(\sqsubset))
$$
\end{lemma}

>>>>

Let $p \rgse p^\prime$ be defined as a union over state relations:
$$
\rgse = \rgse^\mathit{A} \cup  \rgse^\mathit{A^\prime} \cup \rgse^\mathit{W} \cup \rgse^\mathit{W^\prime} \cup \rgse^\mathit{E} \cup \rgse^\mathit{E^\prime} \cup \rgse^\com
$$
where \emph{A} is a field access $\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
\rightarrow \cfgnt{k}\rp$, \emph{W} is a field write $\lp
\cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgnt{*} \rightarrow
\cfgnt{k}\rp$, \emph{E} is a reference compare $\lp
\cfgnt{v}\ \cfgt{=}\ \cfgnt{*} \rightarrow \cfgnt{k}\rp$, the prime symbol
indicates a null reference in the operation or a false outcome, and
\emph{\com} is everything else in the language. Any state relation, say $\rightarrow_x$, is trivially extended to sets of states as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
$$
Let $\hookrightarrow_\gse$ be the extension of $\rgse$ to sets of states.
$$
\rsgse = \hookrightarrow_\gse^\mathit{A}
\cup \hookrightarrow_\gse^\mathit{A^\prime} \cup \hookrightarrow_\gse^\mathit{W} \cup
\hookrightarrow_\gse^\mathit{W^\prime} \cup \hookrightarrow_\gse^\mathit{E} \cup \hookrightarrow_\gse^\mathit{E^\prime}
\cup \hookrightarrow_\gse^\com
$$
The definition embodies the notion of splitting equivalence classes at
certain operations. The set $P$ at a field access for example has two
potential successors: a non-null and null reference. Respectively, the
set $P \rgse^\com P^\prime$ only has a single successor since those expressions
are not related to control flow.

@@

DEFINE $S$ and $S_{FA}$ and unify on the shorthand as $S_A$. 
\begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
If $P \in 2^{S_\mathit{FA}}$ and $q \in S$ are such that $P \sqsubset q$, then $(P\ q)$ is in the functional associated to bisumlation.
\label{lem:access}
$$
\forall P \in 2^{S_\mathit{FA}}\ (P \sqsubset q \Rightarrow (P\ q) \in F_\sim(\sqsubset))
$$
\end{lemma}

### 2014-11-11 tex/heap.tex
Added heap properties

\subsection{Heaps as Bipartite Graphs}
An important aspect, and a novel contribution, of symbolic heaps its
representation as a labeled bipartite graph consisting of
references, $\cfgnt{r}$, and constraint location pairs,
$\lp\phi\ \cfgnt{l}\rp$. The heap structure conveys that the actual
location pointed to by a reference is conditional on aliasing
relationships within the heap. In this way, the graph represents sets
of heaps with the conditions under which those heaps exist.

The machine syntax in \figref{fig:machine-syntax} defines that graph
in $\cfgnt{L}$, the location map, and $\cfgnt{R}$, the reference
map. As done with the environment, $\cfgnt{L}$ and $\cfgnt{R}$ are
treated as partial functions where $\cfgnt{L}(r) =
\{(\phi\ \cfgnt{l})\ ...\}$ is the set of location-constraint pairs in
the heap associated with the given reference, and
$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the reference
associated with the given location-field pair in the heap. Predicate
calculus is used to describe the more complex updates to the heap in
the semantics.

There are several properties of the heap that are invariant and
important to the correctness of the algorithm.
\begin{compactitem}
\item ADD REFERENCES ARE IMMUTABLE
\end{compactitem}

The location $\cfgnt{l}_\mathit{null}$ is a special location in the
heap to represent null. It has a companion reference
$\cfgnt{r}_\mathit{null}$. The initial heap for the machine is defined
such that $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
\{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$

>>>>

\subsection{Heaps as Bipartite Graphs}
An important aspect, and a novel contribution, of a symbolic heap is its
representation as a labeled bipartite graph consisting of
references, $\cfgnt{r}$, and constraint location pairs,
$\lp\phi\ \cfgnt{l}\rp$. The heap structure itself captures that the actual
location pointed to by a reference is conditional on aliasing
relationships within the heap. In this way, the graph represents sets
of heaps with the conditions under which those heaps exist.

The graph is expressed in in $\cfgnt{L}$, the location map, and
$\cfgnt{R}$, the reference map. As done with the environment,
$\cfgnt{L}$ and $\cfgnt{R}$ are treated as partial functions where
$\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the set of
location-constraint pairs in the heap associated with the given
reference, and $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the
reference associated with the given location-field pair in the
heap. Predicate calculus is used to describe the more complex updates
to the heap in the semantics.

There are several properties of the heap that are invariant and
important to the correctness.
\begin{compactitem}
\item \textbf{Immutable references}: a reference does not change in
  the location map; it always points to the same set of constraint
  location pairs.
\item \textbf{Reference partitions}: new references are drawn from
  three distinct partitions $\mathrm{init}_r()$, $\mathrm{fresh}_r()$,
  and $\mathrm{stack}_r()$. The references strictly increase in value
  on each call, and modular arithmetic is used to determine the
  partition to which a reference belongs.
\item \textbf{Determinism}: a reference in  $(\cfgnt{L}\ \cfgnt{R})$ cannot point to two locations at the same time.
\[
\begin{array}{l}
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
\ \ \ \ (\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
\end{array}
\]
$\cfgnt{L}^\leftarrow$ is the pre-image of the location map.
\item \textbf{Type consistent}: every location associated to a reference has the same type.
\[
\begin{array}{l}
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
\ \ \ \ (\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))
\end{array}
\]
\item \textbf{Null and Uninitialized}: The location $\cfgnt{l}_\mathit{null}$ is a special location in the
heap to represent null. It has a companion reference
$\cfgnt{r}_\mathit{null}$. The initial heap for the machine is defined
such that $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
\{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$
\end{compactitem}

### 2014-11-11 tex/javalite.tex
Minor checkpoint
Added heap properties

The state of the Javalite machine (\figref{fig:machine-syntax}),
$\cfgnt{s}$, includes the program registry, a pair of functions
defining the heap $\lp\cfgnt{L}\ \cfgnt{R}\rp$, which is the store, a
constraint, $\phi$, defined over references in the heap, the
environment, $\eta$, for local variables, and the continuation
$\cfgnt{k}$. The more complex structures such as the environment are
defined as lists which start with empty, \cfgnt{mt}. The rewrite rules
that define the semantics treat these lists as partial
functions. As such, $\eta(\cfgnt{x}) = \cfgnt{r}$ is the
reference mapped to the variable $\cfgnt{x}$. The notation
$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
partial function $\eta^\prime$ that is just like $\eta$ only the
variable $\cfgnt{x}$ now maps to $\cfgnt{v}$.

@@

\input{heap}

>>>>

The state of the Javalite machine (\figref{fig:machine-syntax}),
$\cfgnt{s}$, includes the program registry\footnote{The registry $\mu$
  is implied in the rewrite rules rather that states for
  compactness.}, a pair of functions defining the heap
$\lp\cfgnt{L}\ \cfgnt{R}\rp$, which is the store, a constraint,
$\phi$, defined over references in the heap, the environment, $\eta$,
for local variables, and the continuation $\cfgnt{k}$. The more
complex structures such as the environment are defined as lists which
start with empty, \cfgnt{mt}. The rewrite rules that define the
semantics treat these lists as partial functions. As such,
$\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference mapped to the variable
$\cfgnt{x}$. The notation $\eta^\prime = \eta[\cfgnt{x} \mapsto
  \cfgnt{v}]$ defines a new partial function $\eta^\prime$ that is
just like $\eta$ only the variable $\cfgnt{x}$ now maps to
$\cfgnt{v}$.

@@
